An Analysis on the Impact of Local Food Choices

### 2020-03-21 paper_knew.Rmd
New markdown

```{r setup, include=FALSE}
library("ggplot2")
library("naniar")
library("MASS")
library("readxl")
library("sqldf")
library("xtable")
library("sqldf")
library("readr")
library("stargazer")
library("sandwich")
library("lmtest")
library("ggplot2")
library("lindia")
library("gridExtra")

@@

# Dataset Description 
Data we used in this analysis is survey data Food Environment Atlas Dataset, which is published by Economic Research Service, Department of Agriculture.
We have access to this entire survey data which contains records from 2009 to 2016. There are 3100 rows and 275 variables in this dataset including indicators of access to grocery stores at sub-population level, recipients of Supplemental Security Income at the state level, social economics indicators, health indicators, and other indicators that contain data on how local food choices affect diet in the US. 
Variables we used in these research:
Local stores/ food choices:
2009&2014 Convenience Store Availability (count per 1000 population)
2009&2014 Fast-Food Restaurant Availability (count per 1000 population)
2008&2012 WIC-Authorized Store Availability (count per 1000 population)
2009&2014 Supercenters & Club Stores Availability (count per 1000 population)
2009&2014 Specialized Food Store Availability (count per 1000 population)
2009&2016 Farmers’ Market Availability (count per 1000 population)
2009&2014 Grocery Store Availability (count per 1000 population)
2009&2014 Recreation and Fitness Facility Availability (count per 1000 population)
Obesity rate related: 
2008&2013 Adult Obesity Rate (%)
The national free lunch program related:
2010 Price of Low-Fat Milk/National Average (ratio)
2010 Low Access Adults (count per 1000 population)
2010 Low Access Children (count per 1000 population)
2013 Metropolitan Area Indicator
2010 Persistent Poverty Indicator
2010 Persistent Child Poverty Indicator
2015 Child Poverty Rate (%)
2007 Vegetable Acres Harvested (Acres per 1000 population)
2010 SNAP Benefits (Dollars per capita)
2008 WIC Redemptions (Dollars per capita)

@@

## Summary statistics of all the local stores/ food choices variables (on county level)
```{r, my-fig,out.width = '80%', fig.cap = "descriptive statistics", echo = FALSE}
knitr::include_graphics('images/descriptive_food/descriptive.png')
```
As can be seen from the table, Convenience stores got very high values of availabilities per capita, while Supercenters & Club Stores, Specialized Food Stores and Farmers’ Markets got relatively low values.

## Trends of local stores/ food choices
Convenience Store (rest of food choices in appendix): 
```{r, my-fig2,out.width = '90%',echo = FALSE,fig.cap = "convenience store map"}
knitr::include_graphics('/images/tableau_food/1/Dashboard 1.png')
```

@@

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} cccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & Estimate & Std. Error & t value & Pr(\textgreater \textbar t\textbar ) & robust.se \\ 
\hline \\[-1.8ex] 
(Intercept) & $30.238$ & $0.195$ & $155.211$ & $0$ & $0.226$ \\ 
GROCPTH09 & $$-$1.748$ & $0.348$ & $$-$5.021$ & $0$ & $0.449$ \\ 
SUPERCPTH09 & $22.895$ & $3.077$ & $7.440$ & $0$ & $2.885$ \\ 
CONVSPTH09 & $1.586$ & $0.204$ & $7.767$ & $0$ & $0.278$ \\ 
SPECSPTH09 & $$-$6.068$ & $0.829$ & $$-$7.322$ & $0$ & $0.744$ \\ 
WICSPTH08 & $0.932$ & $0.310$ & $3.006$ & $0.003$ & $0.492$ \\ 
FFRPTH09 & $$-$2.203$ & $0.220$ & $$-$10.034$ & $0$ & $0.272$ \\ 
FMRKTPTH09 & $$-$2.013$ & $0.898$ & $$-$2.243$ & $0.025$ & $1.045$ \\ 
RECFACPTH09 & $$-$9.349$ & $0.830$ & $$-$11.261$ & $0$ & $1.047$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

@@

Thus we can see that the following variables are significant using both the robust and the non-robust standard error option:
  - Grocery Stores per thousand (negatively associated)
  - Convenience stores per thousand (positively associated)
  - Full service restaurants per thousand (negatively associated)
  - Per capita WIC redemptions (positively associated)
  - Per capita SNAP benefits (positively associated)
  - Acres of vegetables harvested per thousand (positively associated)
  - Recreation facilities per thousand (negatively associated)
  - Child poverty rate (positively associated)
  - Persistent child poverty indicator (positively associated)
  - Milk price in cents (positively associated) 
  - Number of low access adults per thousand (negatively associated) 
  - Number of low access children per thousand (positively associated)

@@

# Appendix
```{r, my-fig18,out.width = '90%',echo = FALSE,fig.cap = "convenience store map"}
knitr::include_graphics('images/tableau_food/2/Dashboard 1.png')
```

>>>>

```{r setup, include=FALSE}
library("ggplot2")
library("naniar")
library("MASS")
library("readxl")
library("sqldf")
library("xtable")
library("sqldf")
library("readr")
library("stargazer")
library("sandwich")
library("lmtest")
library("ggplot2")
library("lindia")
library("survey")

@@

# Dataset Description 
Data we used in this analysis is survey data Food Environment Atlas Dataset, which is published by Economic Research Service, Department of Agriculture.
We have access to this entire survey data which contains records from 2009 to 2016. There are 3100 rows and 275 variables in this dataset including indicators of access to grocery stores at sub-population level, recipients of Supplemental Security Income at the state level, social economics indicators, health indicators, and other indicators that contain data on how local food choices affect diet in the US.

Variables we used in this research:

Local stores/ food choices:
  - 2009&2014 Convenience Store Availability (count per 1000 population)
  - 2009&2014 Fast-Food Restaurant Availability (count per 1000 population)
  - 2008&2012 WIC-Authorized Store Availability (count per 1000 population)
  - 2009&2014 Supercenters & Club Stores Availability (count per 1000 population)
  - 2009&2014 Specialized Food Store Availability (count per 1000 population)
  - 2009&2016 Farmers’ Market Availability (count per 1000 population)
  - 2009&2014 Grocery Store Availability (count per 1000 population)
  - 2009&2014 Recreation and Fitness Facility Availability (count per 1000 population)

Obesity rate related:

  - 2008&2013 Adult Obesity Rate (%)
  - The national free lunch program related:
  - 2010 Price of Low-Fat Milk/National Average (ratio)
  - 2010 Low Access Adults (count per 1000 population)
  - 2010 Low Access Children (count per 1000 population)
  - 2013 Metropolitan Area Indicator
  - 2010 Persistent Poverty Indicator
  - 2010 Persistent Child Poverty Indicator
  - 2015 Child Poverty Rate (%)
  - 2007 Vegetable Acres Harvested (Acres per 1000 population)
  - 2010 SNAP Benefits (Dollars per capita)
  - 2008 WIC Redemptions (Dollars per capita)

@@

## Summary statistics of all the local stores/ food choices variables (on county level)
```{r, my-fig,out.width = '80%', fig.cap = "descriptive statistics", echo = FALSE}
knitr::include_graphics('images/descriptive_food/descriptive.png')
```

As can be seen from the table, Convenience stores got very high values of availabilities per capita, while Supercenters & Club Stores, Specialized Food Stores and Farmers’ Markets got relatively low values.

## Trends of local stores/ food choices
Convenience Store (rest of food choices in appendix): 
```{r, my-fig2,out.width = '90%',echo = FALSE,fig.cap = "convenience store map"}
knitr::include_graphics('images/tableau_food/1/Dashboard 1.png')
```

@@

@@

The following are the assumptions of the two linear regressions we used:

  - Independence:
A common assumption across all inferential tests is that the observations in the sample are independent from each other. 
  - Normality:
We have county level observations of over 3000 rows. As this value is relatively large, the central limit theorem will take effect and the non-normality does not matter. We also checked the residual qq plot for normality.  
  - Constant Variance for obesity rate:
We assess the plot of residuals vs fitted values, and it shows clear evidence of non-constant variance. There is clearly a pattern of residuals that is undesirable to us. We used robust standard error to try to correct the non-constant variance problem.

@@

Thus we can see that the following variables are significant using both the robust and the non-robust standard error option:

  - Grocery Stores per thousand (negatively associated)
  - Convenience stores per thousand (positively associated)
  - Full service restaurants per thousand (negatively associated)
  - Per capita WIC redemptions (positively associated)
  - Per capita SNAP benefits (positively associated)
  - Acres of vegetables harvested per thousand (positively associated)
  - Recreation facilities per thousand (negatively associated)
  - Child poverty rate (positively associated)
  - Persistent child poverty indicator (positively associated)
  - Milk price in cents (positively associated) 
  - Number of low access adults per thousand (negatively associated) 
  - Number of low access children per thousand (positively associated)

@@

# Appendix
=======
```{r, my-fig18,out.width = '90%',echo = FALSE,fig.cap = "convenience store map"}
knitr::include_graphics('images/tableau_food/2/Dashboard 1.png')
```
